---
title: 'Assignment 1: R'
output: html_document
---
##1.0 Version
```{r}
version
```

##1.1  
Calculate the cube root of 2015
```{r}
2015^(1/3)
```

##1.2 
Find the absolute value of 5.7 minus 6.8 divided by .58
```{r}
abs(5.7-6.8)/.58
```
##1.3 
Create a list of integers from 1 to 12 and call it “a”:
```{r}
a = 1:12
a
```
##1.4 
Create a sequence of odd numbers from 1 to 11:
```{r}
b = c(1, 3, 5, 7, 9, 11)
b
```
##1.5 
Create the same sequence in another way:
```{r}
c = seq(1, 11, 2)
c
```
##1.6 
Take the natural log (ln) of a. (Note that this is done to the entire “vector” called a.)
```{r}
ln.a = log(a)
ln.a
```
##1.7 
Compute the squares of the odd numbers from 1 to 11.
```{r}
sq.c = (c)^2
sq.c
```
##1.8 
Use ?sd to view the help file for the sd function.  What does it do?
```{r}
?sd
```
From the Documentation:
  "This function computes the standard deviation of the values in x. If na.rm is TRUE then missing values are removed before computation proceeds."
  
##1.9. 
Create a variable Name that contains your first name.  Because your name is a character string, not a number, you will need to put it in quotes so that R knows not to go looking for a variable with that name:
```{r}
Name = "Maggie"
paste("My name is", Name)
```

